\documentclass[12pt]{article}

% Package imports
\usepackage{amsmath}    % Math symbols and equations
\usepackage{graphicx}   % Images
\usepackage{url}        % Formatting URLs
\usepackage{hyperref}   % Clickable links in the PDF
\usepackage{fancyhdr}   % Custom headers and footers
\usepackage{geometry}   % For page layout and margins
\geometry{margin=1in}   % 1-inch margins all around
\usepackage{times}      % Times font, common for academic papers
\usepackage{caption}    % Captioning for figures and tables
\usepackage{float}      % Enhanced control over figure and table positioning

% Header and Footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{Your Name}
\fancyhead[R]{Paper Title}
\fancyfoot[C]{\thepage}

% Title Information
\title{Bb}
\author{Chris Ziko, Rakin Munim \\ Department of Computer Science \\ Boston University}
\date{\today}

\begin{document}

% Title Page
\maketitle

% Abstract
\begin{abstract}
This is a masters level culminative paper on research done in CS505. This paper is a repository for ideas, links, and more. 
\end{abstract}

% Keywords
\textbf{Keywords:} music, deep-learning, language-modeling

% Introduction
\section{Introduction}
The introduction provides background on the topic, states the motivation for the work, and briefly describes the structure of the paper.

% Related Work
\section{Related Work}
Discuss previous studies and frameworks related to your topic, including citations. For example, you could refer to a study \cite{raffel2016lakhmidi}.

% Methodology
\section{Methodology}
Describe the methodology used in your research, including any specific techniques or tools applied.

\subsection{Data Collection}
Provide information on the data sources and how data was collected.

\subsection{Data Analysis}
Explain the techniques or algorithms used to analyze the data.

% Results
\section{Results}
Present the findings of your study. Figures and tables are helpful here.

% Sample Figure


% Discussion
\section{Discussion}
Provide insights, interpretations, and implications of the results here.

% Conclusion
\section{Conclusion}
Summarize the main points, highlight the contributions, and suggest directions for future work.

% Acknowledgments (Optional)
\section*{Acknowledgments}
You can include acknowledgments here.

% References
\bibliographystyle{IEEEtran}
\bibliography{anthology,custom}


\end{document}
